On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-17 documents/paper.tex
Texstudio

@@

\bibliographystyle{plainnat}

@@

A poignant summary of the consensus is found in [IEEE C95.1-2005], Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".

@@

\cite{POLAROGRAPHICOXYGENSENSORS}

@@

\bibliography{references}

>>>>

% arara: pdflatex: { shell: yes } 
% arara: biber
% arara: pdflatex: { shell: yes }
% arara: clean: { files: [ test.aux, test.log] }

@@

%\bibliographystyle{plainnat}

@@

A poignant summary of the consensus is found in \cite{instituteofelectricalandelectronicsengineersIEEEC95120052006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".

@@

\clearpage
\printbibliography[heading=none, title={}, keyword={Flagship}]
\printbibliography[heading=none, title={}, keyword={standards}]

@@

%\printbibliography[ title={Other references}]
